### 2021-03-22 README.Rmd
Update README to explain all that it does so far.

>>>>

## What It Does (So Far)

Assuming the latest/development version of [`{stevetemplates}`](https://github.com/svmiller/stevetemplates) (i.e. the one that has the Word template) and considering any potential LaTeX weirdness that comes from different builds, this package has function in R and Make that will:

- simplify the research process to three basic "targets" (in Make): a finished data product to analyze, statistical models of the data, and post-estimation simulations of quantities of interest from the data. These scripts are in the `R/` directory and render to the `data/` directory.
- render your R Markdown document to a fancy PDF document in LaTeX using [my second article template](http://svmiller.com/blog/2020/09/another-rmarkdown-article-template/).
- render your R Markdown document to an anonymized version of that same document. [A post on my blog](http://svmiller.com/blog/2021/03/handle-academic-projects-steveproj-make/) gives clues how to do this with YAML parameters.
- render your R Markdown document to an anonymized Word document. Anonymized Word documents are all that I'm willing to support here. The goal isn't to publish to Word, per se; it's only to produce a document suitable for peer review for journals that demand you provide one.
- farm your R Markdown document for citations and format them to a bibliography file. By default, this will render to a `refs.bib` file in the `inst/` directory. You can tweak this if you like.
- scan your R Markdown document to render a simple title page for peer review. Traditionally, journals ask for a title page (with author information) and a manuscript (without author information). `render_abstract.R` in the `src/` directory is the companion script to `render_pdf-anon.R` in the same directory.
